%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Claudio}{Guerra}
       {Software Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    av. Alcalde Eduardo
    Castillo Velasco
    3620 dep 102
    Ñuñoa
    SCL
    ~
    +56 9 84433323
    +56 2 27245221
    ~
    \href{mailto:claudevandort@gmail.com}{claudevandort@gmail.com}
    \href{https://github.com/claudevandort}{github.com/claudevandort}
  \section{languages}
    bilingual spanish/english
  \section{programming}
    {\color{red} $\varheartsuit$} Python
    PHP, Javascript
    CSS3 \& HTML5
\end{aside}

\section{Interests}

Entrepreneurship, Agile Management, Agile Development, TDD, Continuous Integration, Machine Learning, Neural Networks, Domotics.

\section{Education}

\begin{entrylist}
  \entry
    {2007–2012}
    {Computer Engineering}
    {Universidad Tecnológica de Chile}
    {\emph{}}
\end{entrylist}

\section{Technical Skills}

\begin{itemize}
\item \emph{Languages}: PHP5, Python 2.7, SQL, HTML5, Javascript, Arduino.
\item \emph{Frameworks \& Libraries}: Laravel 4, web.py, NLTK, PySerial, jQuery.
\item \emph{Tools}: Git, PowerDesigner, DIA, \LaTeX, Sublime Text 2, Terminal.
\item \emph{RMDBs}: PostgreSQL, MySQL.
\item \emph{Operating Systems}: Linux (Ubuntu Server), Windows.
\end{itemize}

\section{Experience}

\begin{entrylist}
  \entry
    {02 2012--Now}
    {\href{http://www.smartboxtv.com}{SmartboxTV S.A.}}
    {Providencia, SCL}
    {\emph{Matrix Developer} \\
      Achievements:
      \begin{itemize}
        \item Developed FullPass Admin System \& Services.
        \item Developed {\href{http://www.nunchee.tv}{Nunchee}} Content Manager.
        \item Developed GniusTV, a TV programs recommender system.
        \item Developed Back-end Intelligence of {\href{http://www.smartboxtv.com/products/twitv/}{Trending Channels}} service.
      \end{itemize}}
  \entry
    {08--12 2011}
    {Universidad Tecnológica de Chile}
    {Las Condes, SCL}
    {\emph{Computer Lab Operator}}
  \entry
    {04--06 2011}
    {\href{http://www.techk.cl/}{Tech-Knowledge}}
    {Las Condes, SCL}
    {\emph{Practitioner Web Developer}}
\end{entrylist}

\section{Projects}

\begin{entrylist}
  \entry
    {2013}
    {Thest.me}
    {\href{http://thest.me}{Thest.me}}
    {A network that connects high value idea generators with people interested in developing their ideas.}
  \entry
    {2013}
    {Concertae}
    { }
    {A tool that allows different people to have a digital way to sign informal agreements.}
  \entry
    {2013}
    {DomoLabs}
    { }
    {An initiative to develop low cost products that allows you to control your home remotely.}
\end{entrylist}
%\section{publications}

%Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}
\end{document}